Comparing and combining network-guided biomarker discovery to discover genetic susceptibility mechanisms to breast cancer on the GENESIS study

### 2020-10-16 manuscript/plos/review_1.tex
minor typos fixed

We explored the parameter space of the different methods by running them under different combinations of parameters (Section \ref{methods:parameters}). In agreement with their formulations (Section \ref{methods:methods}), larger values of certain parameters produce less astringent solutions (\nameref{sfig:parameters}A): for HotNet2 and heinz, we examined the threshold to decide each gene has a positive score or zero; for dmGWAS, the \texttt{d} parameter controls how far neighbors could be added; node involved how far the search from the explored subnetwork; for SigMod \texttt{nmax} specifies the maximum size of the solution; and for LEAN, it was the P-value threshold to consider a solution significant. Two parameters had the opposite effect (larger is more stringent): SigMod's \texttt{maxjump}, which sets the threshold to consider an increment in $\lambda$ ``large enough''; and SConES $\eta$, where higher values produce more stringent solutions. However, two of the parameters did not have the expected effect: dmGWAS' \texttt{r}, which controls the minimum increment in the score required to add an additional gene; and SigMod's \texttt{maxjump}, which sets the threshold to consider an increment in $\lambda$ ``large enough''. In both cases, the size of the solution was very similar across the different values. Despite the differences in size, the size of the solutions was relatively robust to the choice of parameters (\nameref{sfig:parameters}B).

>>>>

We explored the parameter space of the different methods by running them under different combinations of parameters (Section \ref{methods:parameters}). In agreement with their formulations (Section \ref{methods:methods}), larger values of certain parameters produce less stringent solutions (\nameref{sfig:parameters}A): for HotNet2 and heinz, this is the threshold above which genes are assigned a non-zero score; for dmGWAS, it is the \texttt{d} parameter, which controls how far neighbors could be added; % node involved how far the search from the explored subnetwork;
for SigMod, it is \texttt{nmax}, which specifies the maximum size of the solution; and for LEAN, it is the P-value threshold to consider a solution significant. Two parameters had the opposite effect (larger is more stringent): SigMod's \texttt{maxjump}, which sets the threshold to consider an increment in $\lambda$ ``large enough''; and SConES's $\eta$, where higher values produce smaller solutions. However, two of the parameters did not have the expected effect: dmGWAS' \texttt{r}, which controls the minimum increment in the score required to add an additional gene; and SigMod's \texttt{maxjump}, which sets the threshold to consider an increment in $\lambda$ ``large enough''. In both cases, the size of the solution was very similar across the different values. Despite the differences in size, the size of the solutions was relatively robust to the choice of parameters (\nameref{sfig:parameters}B).
